ms_figures

### 2024-02-29 ms_figures.Rmd

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(tidyverse)
library(countrycode)
library(circlize)
library(here)
library(ggpubr)
library(kableExtra)
library(DBI)
library(janitor)
library(viridis)
library(broom)
library(exploreARTIS)
library(vegan)
library(tidytext)
library(cowplot)
library(scales)
library(ggsankey)
library(ggpubr)
```

```{r load_data}
# Set directories
datadir <- "outputs"
outdir <- "outputs"
```

@@

fig1a <- fig1a_data %>%
  mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture", "unknown"))) %>%
  ggplot(aes(x = year, y = live_weight_t/1000000, fill = habitat_method)) +
  geom_area() +
  scale_fill_manual(values = habitat_source_colors) +
  labs(y = "Exports\n(mil. t, live weight)", fill = "Source", x = "") +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.title.y = element_text(size = 16),
        axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        legend.text = element_text(size = 9),
        )

@@

fig1b <- ggplot() +
  geom_line(data = fig1b_data, aes(x = year, y = percent_export, color = habitat_method)) +
  scale_color_manual(values = habitat_source_colors) +
  labs(y = "% Production\nExported", x = "", color = "Source") +
  theme_bw() +
  theme(
    text = element_text(size = 16)
  )

@@

## Figure 1 c: Degree or measure of degree distribution by production method and environment

@@

fig1c_out_degree <- fig1c_data %>%
    mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture", "unknown"))) %>%
  ggplot(aes(x = year, y = all_in_degree, color = habitat_method)) +
  geom_smooth() +
  scale_color_manual(values = habitat_source_colors) +
  labs(y = "Average\nno. export partners", color = "Source") + 
  theme_bw() +
  theme(
    text = element_text(size = 16),
    axis.title.x = element_blank()
  )

@@

fig1d <- ggplot() +
  geom_line(data = export_n_countries_concentration_by_source %>% 
      mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture"))), 
      aes(x = year, y = n, color = habitat_method)) +
  geom_line(data = export_n_countries_concentration, aes(x = year, y = n, color = "total"), linewidth = 1) +
  scale_color_manual(values = habitat_source_colors_v2) +
  labs(x = "", y = paste("No. countries\ncomprising ", cumulative_percent_threshold, "% exports", sep = ""), color = "Source") +
  lims(y = c(0, 30)) +
  theme_bw() +
  theme(
    text = element_text(size = 16)
  )

@@

fig1e <- ggplot() +
  geom_line(data = import_n_countries_concentration_by_source %>% 
              mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture", "unknown"))), 
      aes(x = year, y = n, color = habitat_method)) +
  geom_line(data = import_n_countries_concentration, aes(x = year, y = n, color = "total"), linewidth = 1) +
    scale_color_manual(values = habitat_source_colors_v2) +
  labs(x = "", y = paste("No. countries\ncomprising ", cumulative_percent_threshold, "% imports", sep = ""), color = "Source") +
  lims(y = c(0, 30)) +
  theme_bw() +
  theme(
    text = element_text(size = 16)
  )

@@

```{r fig1, fig.height = 4, fig.width = 4}
ggarrange(fig1a,
          ggarrange(fig1b,
                    fig1c_out_degree,
                    ncol = 2, nrow = 1,
                    legend = "none",
                    labels = c("b", "c")),
          ggarrange(fig1d,
                    fig1e,
                    ncol = 2, nrow = 1,
                    legend = "none",
                    labels = c("d", "e")),
          common.legend = TRUE, legend = "bottom",
          ncol = 1, nrow = 3, labels = c("a", ""))

@@

fig2a <- ggplot() +
  geom_area(data = artis_region_method %>% 
                mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture", "unknown"))) %>%
              select(-exporter_importer) %>%
              pivot_longer(exporter_region:importer_region, 
                           names_to = c("flow", "drop"), 
                           values_to = "region", names_sep = "_") %>% 
              filter(flow == "exporter") %>%
              group_by(year, region, habitat_method) %>%
              summarise(live_weight_t = sum(live_weight_t, na.rm = TRUE)), 
            aes(x = year, y = -1*live_weight_t/1000000, fill = habitat_method)) +
  geom_area(data = artis_region_method %>% 
                mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture", "unknown"))) %>%
              select(-exporter_importer) %>%
              pivot_longer(exporter_region:importer_region, 
                           names_to = c("flow", "drop"), 
                           values_to = "region", names_sep = "_") %>% 
              filter(flow == "importer") %>%
              group_by(year, region, habitat_method) %>%
              summarise(live_weight_t = sum(live_weight_t, na.rm = TRUE)), 
            aes(x = year, y = live_weight_t/1000000, fill = habitat_method)) +
  scale_fill_manual(values = habitat_source_colors) +
  geom_hline(yintercept = 0, color = "black", linewidth = 0.5, linetype = "dashed") +
  geom_line(data = region_net_import, aes(x = year, y = net_import/1000000, color = "Net import"), linewidth = 1) +
  scale_color_manual(values = "black") +
  labs(x = "", y = "Trade (million t, live weight)", fill = "Source", color = "") +
  guides(fill = guide_legend(nrow = 2)) +
  theme_bw() +
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        strip.background = element_blank()) +
  facet_wrap(~region, nrow = 1)

@@

```{r fig2a_old, eval=FALSE}
# Imports by Region
fig2a <- artis_region %>% 
  ggplot(aes(x = year, y = live_weight_t/1000000, fill = exporter_region)) +
  geom_area() +
  labs(x = "", y = "", fill = "Exporter") +
  scale_fill_manual(values = region_colors) +
  facet_wrap(~importer_region, nrow = 1) +
  theme_bw() +
  theme(legend.position = "none",
        strip.background = element_blank(),
        strip.text.x = element_blank(),
        axis.text.x = element_blank(),
        plot.margin=unit(c(0.5,0,0,0), "cm"))

```{r fig2b}
# Matrix of plots showcasing inter-regional trade trends
fig2b <- artis_region_method %>% 
    mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture", "unknown"))) %>%
  ggplot(aes(x = year, y = live_weight_t/1000000, fill = habitat_method)) +
  geom_area() +
  scale_fill_manual(values = habitat_source_colors) +
  labs(x = "", y = "Trade (million t, live weight)", color = "Ave. annual change in export \n(1000 t live weight)",
       fill = "Source") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), 
        legend.position = "none",
        strip.background = element_blank(), 
        plot.margin = margin(t = 8, r = 8, l = 2, unit = "mm")) +
  facet_grid(rows = vars(exporter_region), cols = vars(importer_region), 
             labeller = label_wrap_gen(width = 5), scales = "free")

fig2b <- ggdraw(fig2b) +
  draw_label("Exporting region", x = 0.975, y = 0.5, angle = 270) +
  draw_label("Importing region", x = 0.5, y = 0.975)

@@

```{r fig2c_old, eval=FALSE}
# Figure 2c
# Exports by Region
fig2c <- artis_region %>% 
  ggplot(aes(x = year, y = live_weight_t/1000000, fill = importer_region)) +
  geom_area() +
  labs(x = "", y = "", fill = "Importer") +
  scale_fill_manual(values = region_colors) +
  facet_wrap(~exporter_region, ncol = 1) +
  theme_bw() +
  theme(legend.position = "none",
        strip.background = element_blank(),
        strip.text.x = element_blank(),
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        plot.margin=unit(c(0,0.5,0,0), "cm"))

fig2c
```

```{r fig2_old, eval=FALSE}
# Overall Figure 2
ggarrange(ggarrange(fig2a, NULL,
                    ncol = 2, nrow = 1,
                    widths = c(4.5, 1.25), labels = c("a", "")),
          ggarrange(fig2b, 
                    ggarrange(NULL, fig2c,
                              ncol = 1, heights = c(0.3, 4)), 
                    ncol = 2, nrow = 1,
                    widths = c(4.5, 1), labels = c("b", "c")),
          ncol = 1, nrow = 2, 
          heights = c(1, 4.5))

```{r fig2, fig.height=4, fig.width=3}
# Overall Figure 2
ggarrange(ggarrange(fig2a, NULL,
                    ncol = 2, nrow = 1,
                    widths = c(4.5, 0.2), labels = c("a", "")), 
          fig2b, labels = c("", "b"),
          ncol = 1, heights = c(1.75, 4))

@@

fig3a <- fig3a_data %>%
  # Set factor levels
  mutate(habitat_method = factor(habitat_method, levels = c("marine capture", "inland capture",
                                                            "marine aquaculture", "inland aquaculture",
                                                            "unknown" ))) %>%
  ggplot(aes(x = year, y = supply_per_cap, color = habitat_method)) +
  geom_line() + 
  labs(y = "Per capita supply (kg)", x = "", color = "Source") +
  scale_color_manual(values = habitat_source_colors) +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

@@

fig3b <- fig3b_data %>%
   # Set factor levels
  mutate(habitat_method = factor(habitat_method, levels = c("marine capture", "inland capture",
                                                            "marine aquaculture", "inland aquaculture",
                                                            "unknown" ))) %>%
  ggplot(aes(x = year, y = supply_per_cap, fill = habitat_method)) +
  geom_area() + 
  labs(y = "Per capita supply (kg)", x = "", fill = "Source") +
  scale_fill_manual(values = habitat_source_colors) +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        strip.background = element_blank()) +
  facet_wrap(~region)

@@

fig3c <- ggplot() +
  # geom_ribbon(data = fig3c_data %>%
  #               filter(supply_source == "domestic"),
  #             aes(ymin = supply_min_percent, ymax = supply_max_percent, x = year), fill = "grey70") +
  # geom_ribbon(data = fig3c_data %>%
  #               filter(supply_source == "foreign"),
  #             aes(ymin = supply_min_percent, ymax = supply_max_percent, x = year), fill = "grey70") +
  geom_line(data = fig3c_data, aes(x = year, y = supply_percent, color = supply_source)) +
  scale_color_manual(values = c("#F37542", "#0F2D59")) +
  labs(x = "", y = "Percent of supply", color = "Origin") +
  lims(y = c(0,100)) +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

@@

```{r fig3, fig.height = 4, fig.width = 5}
fig3 <- ggarrange(
  ggarrange(fig3a, fig3b, 
            common.legend = TRUE, nrow = 1, widths = c(1, 2),
            labels = c("a", "b")),
  ggarrange(fig3c, fig3d,
            common.legend = TRUE, nrow = 1, widths = c(1, 2),
            labels = c("c", "d")),
  nrow = 2
)

@@

```{r regional_sankey, fig.height = 2, fig.width = 2}
regional_artis <- read.csv(file.path(datadir, "regional_artis_by_source.csv"))
# plot_regional_sankey_method_habitat(regional_artis, 2019, 2019)

@@

marine_cap_p <- marine_cap_regions %>%
  ggplot(aes(x = x, 
               next_x = next_x, 
               node = node, 
               next_node = next_node,
               fill = factor(node),
               value = value,
               label = node)) +
    geom_sankey(flow.alpha = 0.6) +
    scale_fill_manual(values = region_colors) +
    geom_sankey_label(size = 3, color = "white", fill = "gray40") +
    theme_sankey(base_size = 18) +
  labs(x = NULL) +
    #labs(title = "Marine", x = NULL, y = "CAPTURE") +
  theme(
    legend.position = "none",
    axis.text.x = element_blank(),
    plot.title = element_text(hjust = 0.5),
    plot.margin = margin(c(0,0,0,0), unit = "mm")
    )

@@

```{r marine_aqua, fig.height = 2, fig.width = 2}
marine_aqua_regions <- regional_artis %>%
  filter(habitat == "marine" & method == "aquaculture") %>%
  group_by(exporter_region, importer_region) %>%
    summarize(live_weight_t = sum(live_weight_t, na.rm = TRUE)) %>%
    ungroup() %>%
    make_long(exporter_region, importer_region, value = live_weight_t)

@@

marine_aqua_p <- marine_aqua_regions %>%
  ggplot(aes(x = x, 
               next_x = next_x, 
               node = node, 
               next_node = next_node,
               fill = factor(node),
               value = value,
               label = node)) +
    geom_sankey(flow.alpha = 0.6) +
    scale_fill_manual(values = region_colors) +
    geom_sankey_label(size = 3, color = "white", fill = "gray40") +
    theme_sankey(base_size = 18) +
  labs(x = NULL) +
    #labs(title = "Marine", x = NULL, y = "CAPTURE") +
  theme(
    legend.position = "none",
    axis.text.x = element_blank(),
    plot.title = element_text(hjust = 0.5),
    plot.margin = margin(c(0,0,0,0), unit = "mm")
    )

@@

```{r inland_cap, fig.height = 2, fig.width = 2}
inland_cap_regions <- regional_artis %>%
  filter(habitat == "inland" & method == "capture") %>%
  group_by(exporter_region, importer_region) %>%
    summarize(live_weight_t = sum(live_weight_t, na.rm = TRUE)) %>%
    ungroup() %>%
    make_long(exporter_region, importer_region, value = live_weight_t)

@@

inland_cap_p <- inland_cap_regions %>%
  ggplot(aes(x = x, 
               next_x = next_x, 
               node = node, 
               next_node = next_node,
               fill = factor(node),
               value = value,
               label = node)) +
    geom_sankey(flow.alpha = 0.6) +
    scale_fill_manual(values = region_colors) +
    geom_sankey_label(size = 3, color = "white", fill = "gray40") +
    theme_sankey(base_size = 18) +
  labs(x = NULL) +
    #labs(title = "Marine", x = NULL, y = "CAPTURE") +
  theme(
    legend.position = "none",
    axis.text.x = element_blank(),
    plot.title = element_text(hjust = 0.5),
    plot.margin = margin(c(0,0,0,0), unit = "mm")
    )

@@

```{r inland_aqua, fig.height = 2, fig.width = 2}
inland_aqua_regions <- regional_artis %>%
  filter(habitat == "inland" & method == "aquaculture") %>%
  group_by(exporter_region, importer_region) %>%
    summarize(live_weight_t = sum(live_weight_t, na.rm = TRUE)) %>%
    ungroup() %>%
    make_long(exporter_region, importer_region, value = live_weight_t)

@@

inland_aqua_p <- inland_aqua_regions %>%
  ggplot(aes(x = x, 
               next_x = next_x, 
               node = node, 
               next_node = next_node,
               fill = factor(node),
               value = value,
               label = node)) +
    geom_sankey(flow.alpha = 0.6) +
    scale_fill_manual(values = region_colors) +
    geom_sankey_label(size = 3, color = "white", fill = "gray40") +
    theme_sankey(base_size = 18) +
  labs(x = NULL) +
    #labs(title = "Marine", x = NULL, y = "CAPTURE") +
  theme(
    legend.position = "none",
    axis.text.x = element_blank(),
    plot.title = element_text(hjust = 0.5),
    plot.margin = margin(c(0,0,0,0), unit = "mm")
    )

inland_aqua_p
```
```{r regional_sankey_by_source, fig.height = 2.5, fig.width = 3}
ggarrange(marine_cap_p, inland_cap_p,
            marine_aqua_p, inland_aqua_p,
            ncol = 2, nrow = 2,
          labels = c("a", "b", "c", "d"))
          # labels = c("Marine Capture", "Inland Capture",
          #            "Marine Aquaculture", "Inland Aquaculture"))

@@

```{r si_top_exporters, fig.height = 5, fig.width = 4}

top_exporters_old <- read.csv(file.path(datadir, "top_exporters_old.csv")) %>%
  mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture", "unknown")))
top_exporters_recent <- read.csv(file.path(datadir, "top_exporters_recent.csv")) %>%
  mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture", "unknown")))

exporters_old_plot <- top_exporters_old %>%
  ggplot(aes(x = live_weight_t/1000000, y = reorder(exporter_iso3c, ranking), fill = habitat_method)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = habitat_source_colors) +
  scale_y_reordered() +
  labs(y = "", x = "Live weight (million t)") +
  xlim(c(0,6)) +
  facet_wrap(~habitat_method, ncol = 1, scales = "free_y") +
  theme_minimal() +
  theme(legend.position = "none")

exporters_recent_plot <- top_exporters_recent %>%
  ggplot(aes(x = live_weight_t/1000000, y = reorder(exporter_iso3c, ranking), fill = habitat_method)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = habitat_source_colors) +
  scale_y_reordered() +
  labs(y = "", x = "Live weight (million t)") +
  facet_wrap(~habitat_method, ncol = 1, scales = "free_y") +
  theme_minimal() +
  theme(legend.position = "none")

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
library(tidyverse)
library(countrycode)
library(circlize)
library(here)
library(ggpubr)
library(kableExtra)
library(DBI)
library(janitor)
library(viridis)
library(broom)
library(exploreARTIS)
library(vegan)
library(tidytext)
library(cowplot)
library(scales)
library(ggsankey)
library(ggpubr)
```

```{r load_data}
# Set directories
datadir <- "qa/outputs_20240221"
outdir <- "qa/outputs_20240221"
```

@@

fig1a <- fig1a_data %>%
  mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture", "unknown"))) %>%
  ggplot(aes(x = year, y = live_weight_t/1000000, fill = habitat_method)) +
  geom_area() +
  scale_fill_manual(values = habitat_source_colors) +
  labs(y = "Exports\n(mil. t, live weight)", fill = "Source", x = "") +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.title.y = element_text(size = 12),
        axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        legend.title = element_text(size = 7),
        legend.text = element_text(size = 6)
        )

@@

fig1b <- ggplot() +
  geom_line(data = fig1b_data, aes(x = year, y = percent_export, color = habitat_method)) +
  scale_color_manual(values = habitat_source_colors) +
  labs(y = "% Production\nexported", x = "", color = "Source") +
  theme_bw() +
  theme(
    text = element_text(size = 10),
    legend.title = element_text(size = 7),
    legend.text = element_text(size = 6)
  )

@@

## Figure 1c: Degree or measure of degree distribution by production method and environment

@@

fig1c_out_degree <- fig1c_data %>%
    mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture", "unknown"))) %>%
  ggplot(aes(x = year, y = all_in_degree, color = habitat_method)) +
  geom_smooth(alpha = 0.2) +
  scale_color_manual(values = habitat_source_colors) +
  labs(y = "Average\nno. export partners", color = "Source") + 
  theme_bw() +
  theme(
    text = element_text(size = 10),
    axis.title.x = element_blank(),
    legend.title = element_text(size = 7),
    legend.text = element_text(size = 6)
  )

@@

fig1d <- ggplot() +
  geom_line(data = export_n_countries_concentration_by_source %>% 
      mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture"))), 
      aes(x = year, y = n, color = habitat_method)) +
  geom_line(data = export_n_countries_concentration, aes(x = year, y = n, color = "total"), linewidth = 1) +
  scale_color_manual(values = habitat_source_colors_v2) +
  labs(x = "", y = paste("No. countries\ncomprising ", cumulative_percent_threshold, "% exports", sep = ""), color = "Source") +
  lims(y = c(0, 30)) +
  theme_bw() +
  theme(
    text = element_text(size = 10),
    legend.title = element_text(size = 7),
    legend.text = element_text(size = 6)
  )

@@

fig1e <- ggplot() +
  geom_line(data = import_n_countries_concentration_by_source %>% 
              mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture", "unknown"))), 
      aes(x = year, y = n, color = habitat_method)) +
  geom_line(data = import_n_countries_concentration, aes(x = year, y = n, color = "total"), linewidth = 1) +
    scale_color_manual(values = habitat_source_colors_v2) +
  labs(x = "", y = paste("No. countries\ncomprising ", cumulative_percent_threshold, "% imports", sep = ""), color = "Source") +
  lims(y = c(0, 30)) +
  theme_bw() +
  theme(
    text = element_text(size = 10),
    legend.title = element_text(size = 7),
    legend.text = element_text(size = 6)
  )

@@

```{r fig1, fig.height = 6, fig.width = 6}
ggarrange(fig1a,
          ggarrange(fig1b,
                    fig1c_out_degree,
                    ncol = 2, nrow = 1,
                    legend = "none",
                    labels = c("b", "c")),
          ggarrange(fig1d,
                    fig1e,
                    ncol = 2, nrow = 1,
                    legend = "none",
                    labels = c("d", "e")),
          common.legend = TRUE, legend = "bottom",
          ncol = 1, nrow = 3, labels = c("a", ""))

@@

fig2a <- ggplot() +
  geom_area(data = artis_region_method %>% 
                mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture", "unknown"))) %>%
              select(-exporter_importer) %>%
              pivot_longer(exporter_region:importer_region, 
                           names_to = c("flow", "drop"), 
                           values_to = "region", names_sep = "_") %>% 
              filter(flow == "exporter") %>%
              group_by(year, region, habitat_method) %>%
              summarise(live_weight_t = sum(live_weight_t, na.rm = TRUE)), 
            aes(x = year, y = -1*live_weight_t/1000000, fill = habitat_method)) +
  geom_area(data = artis_region_method %>% 
                mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture", "unknown"))) %>%
              select(-exporter_importer) %>%
              pivot_longer(exporter_region:importer_region, 
                           names_to = c("flow", "drop"), 
                           values_to = "region", names_sep = "_") %>% 
              filter(flow == "importer") %>%
              group_by(year, region, habitat_method) %>%
              summarise(live_weight_t = sum(live_weight_t, na.rm = TRUE)), 
            aes(x = year, y = live_weight_t/1000000, fill = habitat_method)) +
  scale_fill_manual(values = habitat_source_colors) +
  geom_hline(yintercept = 0, color = "black", linewidth = 0.5, linetype = "dashed") +
  geom_line(data = region_net_import, aes(x = year, y = net_import/1000000, color = "Net import"), linewidth = 1) +
  scale_color_manual(values = "black") +
  labs(x = "", y = "Trade (million t, live weight)", fill = "Source", color = "") +
  guides(fill = guide_legend(nrow = 2)) +
  theme_bw() +
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        strip.background = element_blank(),
        plot.margin = unit(c(t=0, r=1, b=0, l=0.5), "cm")) +
  facet_wrap(~region, nrow = 1)

fig2a <- ggdraw(fig2a) +
  draw_label("Net import", x = 0.97, y = 0.55, angle = 270, size = 9) +
  draw_label("Net export", x = 0.97, y = 0.3, angle = 270, size = 9)

@@

```{r fig2b}
# Matrix of plots showcasing inter-regional trade trends
fig2b <- artis_region_method %>% 
    mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture", "unknown"))) %>%
  ggplot(aes(x = year, y = live_weight_t/1000000, fill = habitat_method)) +
  geom_area() +
  scale_fill_manual(values = habitat_source_colors) +
  scale_y_continuous(position = "right") +
  labs(x = "", y = "", color = "Ave. annual change in export \n(1000 t live weight)",
       fill = "Source") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        legend.position = "none",
        strip.background = element_blank(),
        plot.margin = margin(t = 6, r = 7, l = 6, unit = "mm")) +
  facet_grid(rows = vars(exporter_region), cols = vars(importer_region), 
             labeller = label_wrap_gen(width = 5), scales = "free", switch = "y")

fig2b <- ggdraw(fig2b) +
  draw_label("Exporting region", x = 0.02, y = 0.5, angle = 90, size = 10) +
  draw_label("Importing region", x = 0.5, y = 0.965, size = 10) +
  draw_label("Trade (million t, live weight)", x = 0.96, y = 0.5, angle = 270, size = 10)

@@

```{r fig2, fig.height=8, fig.width=6.5}
# Overall Figure 2
ggarrange(ggarrange(fig2a, NULL,
                    ncol = 2, nrow = 1,
                    widths = c(4.5, 0.2), labels = c("a", "")), 
          fig2b, labels = c("", "b"),
          ncol = 1, heights = c(3, 4))

@@

fig3a <- fig3a_data %>%
  # Set factor levels
  mutate(habitat_method = factor(habitat_method, levels = c("marine capture", "inland capture",
                                                            "marine aquaculture", "inland aquaculture",
                                                            "unknown" ))) %>%
  ggplot(aes(x = year, y = supply_per_cap, color = habitat_method)) +
  geom_line() + 
  labs(y = "Per capita supply (kg)", x = "", color = "Source") +
  scale_color_manual(values = habitat_source_colors) +
  guides(color = guide_legend(nrow = 1)) +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

@@

fig3b <- fig3b_data %>%
   # Set factor levels
  mutate(habitat_method = factor(habitat_method, levels = c("marine capture", "inland capture",
                                                            "marine aquaculture", "inland aquaculture",
                                                            "unknown" ))) %>%
  ggplot(aes(x = year, y = supply_per_cap, fill = habitat_method)) +
  geom_area() + 
  labs(y = "Per capita supply (kg)", x = "", fill = "Source") +
  scale_fill_manual(values = habitat_source_colors) +
  guides(fill = guide_legend(nrow = 1)) +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        strip.background = element_blank()) +
  facet_wrap(~region)

@@

fig3c <- ggplot() +
  geom_line(data = fig3c_data, aes(x = year, y = supply_percent, color = supply_source)) +
  scale_color_manual(values = c("#F37542", "#0F2D59")) +
  labs(x = "", y = "Percent of supply", color = "Origin") +
  lims(y = c(0,100)) +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

@@

```{r fig3, fig.height = 6, fig.width = 7}
fig3 <- ggarrange(
  ggarrange(fig3a, fig3b, 
            common.legend = TRUE, nrow = 1, widths = c(1, 2),
            labels = c("a", "b")),
  ggarrange(fig3c, fig3d,
            common.legend = TRUE, nrow = 1, widths = c(1, 2),
            labels = c("c", "d")),
  nrow = 2
)

@@

```{r regional_sankey, fig.height = 3, fig.width = 3}
regional_artis <- read.csv(file.path(datadir, "regional_artis_by_source.csv"))

@@

marine_cap_p <- marine_cap_regions %>%
  ggplot(aes(x = x, 
               next_x = next_x, 
               node = node, 
               next_node = next_node,
               fill = factor(node),
               value = value,
               label = node)) +
    geom_sankey(flow.alpha = 0.6) +
    scale_fill_manual(values = region_colors) +
    geom_sankey_label(size = 4, color = "white", fill = "gray40") +
    theme_sankey(base_size = 18) +
  labs(x = NULL) +
    #labs(title = "Marine", x = NULL, y = "CAPTURE") +
  theme(
    legend.position = "none",
    axis.text.x = element_blank(),
    plot.title = element_text(hjust = 0.5),
    plot.margin = margin(c(t=-0.5, r=-10, b=-1, l=-18), unit = "mm")
    )

marine_cap_p <- ggdraw(marine_cap_p) +
  draw_label("Marine capture", x = 0.5, y = 0.97, size = 9)

@@

```{r marine_aqua, fig.height = 3, fig.width = 3}
marine_aqua_regions <- regional_artis %>%
  filter(habitat == "marine" & method == "aquaculture") %>%
  group_by(exporter_region, importer_region) %>%
    summarize(live_weight_t = sum(live_weight_t, na.rm = TRUE)) %>%
    ungroup() %>%
    make_long(exporter_region, importer_region, value = live_weight_t)

@@

marine_aqua_p <- marine_aqua_regions %>%
  ggplot(aes(x = x, 
               next_x = next_x, 
               node = node, 
               next_node = next_node,
               fill = factor(node),
               value = value,
               label = node)) +
    geom_sankey(flow.alpha = 0.6) +
    scale_fill_manual(values = region_colors) +
    geom_sankey_label(size = 4, color = "white", fill = "gray40") +
    theme_sankey(base_size = 18) +
  labs(x = NULL) +
    #labs(title = "Marine", x = NULL, y = "CAPTURE") +
  theme(
    legend.position = "none",
    axis.text.x = element_blank(),
    plot.title = element_text(hjust = 0.5),
    plot.margin = margin(c(t=-0.5, r=-10, b=-1, l=-18), unit = "mm")
    )

marine_aqua_p <- ggdraw(marine_aqua_p) +
  draw_label("Marine aquaculture", x = 0.5, y = 0.97, size = 9)

@@

```{r inland_cap, fig.height = 3, fig.width = 3}
inland_cap_regions <- regional_artis %>%
  filter(habitat == "inland" & method == "capture") %>%
  group_by(exporter_region, importer_region) %>%
    summarize(live_weight_t = sum(live_weight_t, na.rm = TRUE)) %>%
    ungroup() %>%
    make_long(exporter_region, importer_region, value = live_weight_t)

@@

inland_cap_p <- inland_cap_regions %>%
  ggplot(aes(x = x, 
               next_x = next_x, 
               node = node, 
               next_node = next_node,
               fill = factor(node),
               value = value,
               label = node)) +
    geom_sankey(flow.alpha = 0.6) +
    scale_fill_manual(values = region_colors) +
    geom_sankey_label(size = 4, color = "white", fill = "gray40") +
    theme_sankey(base_size = 18) +
  labs(x = NULL) +
    #labs(title = "Marine", x = NULL, y = "CAPTURE") +
  theme(
    legend.position = "none",
    axis.text.x = element_blank(),
    plot.title = element_text(hjust = 0.5),
    plot.margin = margin(c(t=-0.5, r=-18, b=-1, l=-18), unit = "mm")
    )

inland_cap_p <- ggdraw(inland_cap_p) +
  draw_label("Inland capture", x = 0.5, y = 0.97, size = 9)

@@

```{r inland_aqua, fig.height = 3, fig.width = 3}
inland_aqua_regions <- regional_artis %>%
  filter(habitat == "inland" & method == "aquaculture") %>%
  group_by(exporter_region, importer_region) %>%
    summarize(live_weight_t = sum(live_weight_t, na.rm = TRUE)) %>%
    ungroup() %>%
    make_long(exporter_region, importer_region, value = live_weight_t)

@@

inland_aqua_p <- inland_aqua_regions %>%
  ggplot(aes(x = x, 
               next_x = next_x, 
               node = node, 
               next_node = next_node,
               fill = factor(node),
               value = value,
               label = node)) +
    geom_sankey(flow.alpha = 0.6) +
    scale_fill_manual(values = region_colors) +
    geom_sankey_label(size = 4, color = "white", fill = "gray40") +
    theme_sankey(base_size = 18) +
  labs(x = NULL, title = NULL) +
  theme(
    legend.position = "none",
    axis.text.x = element_blank(),
    plot.title = element_text(hjust = 0.5, size = 9),
    plot.margin = margin(c(t=-0.5, r=-18, b=-1, l=-18), unit = "mm")
    )

inland_aqua_p <- ggdraw(inland_aqua_p) +
  draw_label("Inland aquaculture", x = 0.5, y = 0.97, size = 9)

inland_aqua_p
```
```{r regional_sankey_by_source, fig.height = 8, fig.width = 10}
ggarrange(marine_cap_p, inland_cap_p,
            marine_aqua_p, inland_aqua_p,
            ncol = 2, nrow = 2,
          labels = c("a", "b", "c", "d"))

@@

```{r si_top_exporters, fig.height = 7, fig.width = 6}

top_exporters_old <- read.csv(file.path(datadir, "si_top_exporters_old_fill.csv")) %>%
  mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture", "unknown")))
top_exporters_recent <- read.csv(file.path(datadir, "si_top_exporters_recent_fill.csv")) %>%
  mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture", "unknown")))

exporters_old_plot <- top_exporters_old %>%
  pivot_longer(cols = c("domestic", "foreign"), names_to = "dom_source", values_to = "live_weight_t_2") %>%
  ggplot(aes(x = live_weight_t_2/1000000, y = reorder(exporter_iso3c, ranking), fill = dom_source)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = habitat_source_colors) +
  scale_y_reordered() +
  labs(y = "", x = "Live weight (million t)", fill = "Export Source") +
  xlim(c(0,6)) +
  facet_wrap(~habitat_method, ncol = 1, scales = "free_y") +
  theme_minimal() +
  theme(
    legend.position = "none",
    axis.text = element_text(size = 8)
  )
